### 2014-10-23 paper/include/dtail.tex

Cui et al. \cite{dtail} propose DTail. They evaluate two versions of DTail referenced as DTail-R and DTail-V utilizing Retention Time and Validity information, respectively. Even so, their main idea is that more types of refresh information can be incorporated and stored together with the Retention time and Validity information. DTail can then choose the most efficient refresh schema depending on the current situation, i.e. workload and type of application. Refresh data is kept per row and is stored in the DRAM itself instead of storing it in the MC which many other solutions do \cite{raidr}\cite{smartrefresh}\cite{refrint}. To counter the added latency of a slower memory, Cui et al. utilizes spatial locality of the refresh data and performs prefetching into a FIFO buffer. As the refresh data is kept on a row level DTail can save more refreshes than other techniques that have a lower granularity.

>>>>

Cui et al. \cite{dtail} propose DTail. They evaluate two versions of DTail referenced as DTail-R and DTail-V utilizing R and V information, respectively. Even so, their main idea is that more types of  information can be incorporated and stored together with the R and V information. DTail can then choose the most efficient refresh schema depending on the current situation, i.e. workload and type of application. How acquisition of the \textit{refresh data} is to be performed is left as future work. Refresh data is kept per row and is stored in the DRAM itself instead of in the MC which many other solutions do \cite{raidr}\cite{smartrefresh}\cite{refrint}. To counter the added latency of a slower memory (DRAM versus fast memory in the MC), Cui et al. utilizes spatial locality of the RV information and performs prefetching into a FIFO buffer. As the refresh data is kept on a row level DTail can save more refreshes than other techniques that have a lower granularity.

### 2014-10-23 paper/include/rioparis.tex

As mentioned earlier, RIO and PARIS can be combined, which results in PARIS removing unnecessary refreshes and RIO lowering the rate at which the performed refreshes are done. This is similar to what Cui et al. does with DTail-RV. Cui et al. manages to lower the number of refreshes somewhat more than Baek et al. does with RIO and PARIS. The difference comes from DTail-V performing better than PARIS both due to DTail keeping Validity information per row instead of per group of rows, and that DTail switches between CBR and ROR which PARIS does not do. RIO and DTail-R performs similar but RIO have a bigger storage overhead. DTail requires changes to the MC while RIO and PARIS is implemented in software and thus are more easy to realize.

>>>>

As mentioned earlier, RIO and PARIS can be combined, which results in PARIS removing unnecessary refreshes and RIO lowering the rate at which the performed refreshes are done. This is similar to what Cui et al. does with DTail-RV. Cui et al. manages to lower the number of refreshes somewhat more than Baek et al. does with RIO and PARIS. The difference comes from DTail-V performing better than PARIS both due to DTail keeping Validity information per row instead of per group of rows, and that DTail switches between CBR and ROR which PARIS does not do. Looking at RIO and DTail-R instead, they performs similar but RIO have a bigger storage overhead. DTail requires changes to the MC and the DDRx standard whereas a combination of RIO and PARIS would need to modify the MC and the OS.
